Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest

Figure~\ref{fig:tas} goes on how to implement mutual exclusion for
a set of $N$ processes.
It uses $N+1$ variables.
Variable \texttt{shared} is initialized to \texttt{False} while
\texttt{private[$i$]} for each process $i$ is initialized to \texttt{True}.
An important invariant, $I_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $I_2(i)$, is that if process $i$ is in the critical section,
then \texttt{private[$i$] == False}.
Between the two (i.e., $I_1 \land \forall i: I_2(i)$),
it is clear that only one process can be in the
critical section at the same time.

@@

In Figure~\ref{fig:tas} we have shown a solution based on a shared
variable and a private variable for each process.   The private
variables themselves are implemented as shared variables as well,
but they are accessed only by their respective processes.
There is no need to keep \texttt{private} as a shared
variable---we only did so to be able to show and check the invariants.
Figure~\ref{fig:tas2} shows a more straightforward implementation.
The solution is similar to the na\"{i}ve solution of Figure~\ref{fig:uplock},
but uses test-and-set to check and set the lock variable atomically.
Compared to Peterson's Algorithm, this approach is general for
any number of processes.

>>>>

Figure~\ref{fig:tas} goes on how to implement mutual exclusion for
a set of $N$ processes.
It is called \emph{spinlock}, because each process is ``spinning'' until
it can acquire the lock.
The program uses $N+1$ variables.
Variable \texttt{shared} is initialized to \texttt{False} while
\texttt{private[$i$]} for each process $i$ is initialized to \texttt{True}.
An important invariant, $I_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $I_2(i)$, is that if process $i$ is in the critical section,
then \texttt{private[$i$] == False}.
Between the two (i.e., $I_1 \land \forall i: I_2(i)$),
it is clear that only one process can be in the
critical section at the same time.

@@

In Figure~\ref{fig:tas} we have shown a solution based on a shared
variable and a private variable for each process.   The private
variables themselves are actually implemented as shared variables,
but they are accessed only by their respective processes.
There is no need to keep \texttt{private} as a shared
variable---we only did so to be able to show and check the invariants.
Figure~\ref{fig:tas2} shows a more straightforward implementation of spinlock.
The solution is similar to the na\"{i}ve solution of Figure~\ref{fig:uplock},
but uses test-and-set to check and set the lock variable atomically.
This approach is general for any number of processes.
